\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amssymb}
\title{Homework - 1}
\author{Thuan Nguyen - Thai Tang - Khuong Dinh - Hung Vo - Long Trieu}
\begin{document}

\maketitle

\section*{Exercise 1}
Assuming we have a generic 2x2 matrix as below.
\[
\begin{bmatrix}
    a & b \\
    c & d \\
\end{bmatrix}
\]

To find the eigenvalues of the matrix \( A = \begin{bmatrix} a & b \\ c & d \end{bmatrix} \), we solve the characteristic equation obtained from the determinant of \( A - \lambda I \), where \( I \) is the identity matrix:

\[
\text{det}(A - \lambda I) = \begin{vmatrix} a - \lambda & b \\ c & d - \lambda \end{vmatrix} = (\lambda^2 - (a+d)\lambda + (ad-bc))
\]

So, finding the eigenvalues is equivalent to solving the following equation: \( \lambda^2 - (a+d)\lambda + (ad-bc) = 0 \).

Once we have the eigenvalues \( \lambda_1, \lambda_2 \), we can find the corresponding eigenvectors \( x_1, x_n \) by solving the system of linear equations \( (A - \lambda_i I)x_i = 0 \) for each \( i \):

\[
(A - \lambda_i I)x_i = \begin{bmatrix} a - \lambda_i & b \\ c & d - \lambda_i \end{bmatrix} \begin{bmatrix} x_{i1} \\ x_{i2} \end{bmatrix} = \begin{bmatrix} 0 \\ 0 \end{bmatrix}
\]

If \(c\) is not zero, and the eigenvalues are \(\lambda_1\) and \(\lambda_2\), the corresponding eigenvectors can be expressed as:

For \(\lambda_1\):
\[
x_1 = \begin{bmatrix} \lambda_1 - d \\ c \end{bmatrix}
\]

For \(\lambda_2\):
\[
x_2 = \begin{bmatrix} \lambda_2 - d \\ c \end{bmatrix}
\]

If \( b \) is not zero, and the eigenvalues are \( \lambda_1 \) and \( \lambda_2 \), the corresponding eigenvectors can be expressed as:

For \( \lambda_1 \):
\[
x_1 = \begin{bmatrix} b \\ \lambda_1 - a \end{bmatrix}
\]

For \( \lambda_2 \):
\[
x_2 = \begin{bmatrix} b \\ \lambda_2 - a \end{bmatrix}
\]

If both \( b \) and \( c \) are zero, and the eigenvalues are \( \lambda_1 \) and \( \lambda_2 \), the corresponding eigenvectors are:

For \( \lambda_1 \):
\[
x_1 = \begin{bmatrix} 1 \\ 0 \end{bmatrix}
\]

For \( \lambda_2 \):
\[
x_2 = \begin{bmatrix} 0 \\ 1 \end{bmatrix}
\]

Finally, the formula for an inverse matrix is as follows:

\[
A^{-1} = \frac{1}{ad - bc} \begin{bmatrix} d & -b \\ -c & a \end{bmatrix}
\]

Applying the formulas above.

- For \( A = \begin{bmatrix} 1 & 2 \\ 0 & 3 \end{bmatrix} \), \( \lambda^2 - 4\lambda + 3 = 0 \)

\[
\begin{aligned}
    \lambda_1 &= 1 \\
    \lambda_2 &= 3 \\
\end{aligned}
\]

Since b is not zero so \( X = \begin{bmatrix} 2 & 2 \\ 0 & 2 \end{bmatrix} = \begin{bmatrix} 1 & 1 \\ 0 & 1 \end{bmatrix} \)

\[
X^{-1} = \frac{1}{(1)(1) - (1)(0)} \begin{bmatrix} 1 & -1 \\ 0 & 1 \end{bmatrix} = \begin{bmatrix} 1 & -1 \\ 0 & 1 \end{bmatrix}
\]

- For \( A = \begin{bmatrix} 1 & 1 \\ 3 & 3 \end{bmatrix} \), \( \lambda^2 - 4\lambda = 0 \)

\[
\begin{aligned}
    \lambda_1 &= 0 \\
    \lambda_2 &= 4 \\
\end{aligned}
\]

Since b is not zero so \( X = \begin{bmatrix} 1 & 1 \\ -1 & 3 \end{bmatrix} \)

\[
X^{-1} = \frac{1}{(1)(3) - (-1)(1)} \begin{bmatrix} 3 & -1 \\ 1 & 1 \end{bmatrix} = \begin{bmatrix} 3/4 & -1/4 \\ 1/4 & 1/4 \end{bmatrix}
\]

\[
A^{3} = X\Lambda^{3}X^{-1}
\]

\[ A^{-1} = X \Lambda^{-1} X^{-1} \], because \[ A^{-1} A = X \Lambda^{-1} X^{-1} X \Lambda X^{-1} = X \Lambda^{-1} I \Lambda X^{-1} = X I X^{-1} = I \]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Exercise 3}

We can replace the fact that \( A = X \Lambda X^{-1} \) and \( I = X X^{-1} \) into \( A + 2I \), we will have:

\[
A + 2I = X \Lambda X^{-1} + 2 X X^{-1}
= X (\Lambda + 2I) X^{-1}
\]

So, the eigenvalue matrix is \( \Lambda + 2I \), the eigenvector matrix is \( X \).
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Exercise 4}
(a) False. Even if all eigenvectors of \(A\) are linearly independent, some still can correspond to eigenvalue \(\lambda = 0\). Because the determinant of the matrix \(A\) is the product of its eigenvalues, we have \(\det(A) = 0\), which implies that \(A\) cannot be invertible.
\\
(b) True. Because we have \(n\) independent eigenvectors that can form a basis \(\mathbb{R}^n\) for matrix \(A \in \mathbb{R}^{n \times n}\), it follows that \(A\) is diagonalizable.
\\
(c) True. Because all the columns of \(X\) are independent, \(X\) is a full-rank matrix, which implies that \(X\) can be inverted.
\\
(d) False. Not enough to draw a conclusion, because there are invertible matrices can not be diagonalize.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Exercise 6}
\[
A=
  \begin{bmatrix}
    4 & 0 \\
    1 & 2 
  \end{bmatrix}
\]
$\det(\lambda I-A) = 0$ \\
$\Rightarrow \det\left( 
\begin{bmatrix}
    1 & 0 \\
    0 & 1 
\end{bmatrix} -
\begin{bmatrix}
    4 & 0 \\
    1 & 2 
\end{bmatrix}\right) = 
\begin{bmatrix}
    \lambda - 4  & 0 \\
    0 & \lambda -2 
\end{bmatrix} = 0.$
So there are two roots: \\
$\lambda = 2$ or $\lambda = 4$.    
\\
\\
Find eigenvectors for $\lambda = 4$. Find all vectors $X \neq 0$ such that $AX = 4X$.
\\
We have:
$(4I - A) X = 0 \Rightarrow X =   
\begin{bmatrix}
    4 & 0 \\
    1 & 0 
\end{bmatrix}
\begin{bmatrix}
    x  \\
    y  
\end{bmatrix} = \begin{bmatrix}
    0  \\
    0  
\end{bmatrix} \Rightarrow y = 0 \Rightarrow x = \begin{bmatrix}
2i  \\
i  
\end{bmatrix}$
\\
\\
Find eigenvectors for $\lambda = 2$. Find all vectors $X \neq 0$ such that $AX = 2X$.
\\
We have:
$(2I - A) X = 0 \Rightarrow X =   
\begin{bmatrix}
    2 & 0 \\
    1 & 0 
\end{bmatrix}
\begin{bmatrix}
    x  \\
    y  
\end{bmatrix} = \begin{bmatrix}
    0  \\
    0  
\end{bmatrix} \Rightarrow y = 0 \Rightarrow x = \begin{bmatrix}
i  \\
0  
\end{bmatrix}$
\\
$\Rightarrow S = \begin{bmatrix}
2 & 0  \\
1 & 1  
\end{bmatrix}$.
Having that $A = X \cap X^{-1} = X^{-1} \cap (X^{-1})^{-1}.$
\\ We can conclude that all the matrices are diagonal. $A^{-1}$ are the inverse matrices $X^{-1}$ of matrix $X$.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Exercise 11}
(a) True. \(\det(A) = \lambda_1 \lambda_2 \lambda_3 = 2 \times 2 \times 5 \neq 0\) \(\Rightarrow\) \(A\) can be invertible.
\\
(b) False. Because we have 2 eigenvalues with the same value, we lack independent eigenvectors to form a basis \(\mathbb{R}^n\).
\\
(c) True.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Exercise 12}
(a) False. Multiples of $(1,4)$ eigenvector could respond to a nonzero eigenvalue $\Rightarrow$ $\det(A) \neq 0$ $\Rightarrow$ $A$ is invertible.
\\
(b) True. If not, we would have distinct (independent) eigenvectors.
\\
(c) True, since there are not enough independent eigenvectors $\Rightarrow$ eigenvector matrix $X$ is not invertible $\Rightarrow$ $A$ is not diagonalizable.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section*{Exercise 13}
With \(A=\begin{bmatrix}8 & 0 \\ 0 & 2 \end{bmatrix}\), we need to find \(x\) and \(y\) to fill in the matrix \(A=\begin{bmatrix} 8 & x \\ y & 2 \end{bmatrix}\). 

Because we know that \(A\) has a repeated eigenvalue \(\lambda = 5\), we can calculate \(\det(A - \lambda I) = (\lambda - 5)^2\). This yields the equation \((8 - \lambda) \times (2 - \lambda) - x \times y = (\lambda - 5)^2\).

\(\rightleftharpoons\) \(x \times y = -9\) \(\rightleftharpoons\)  (\(x = -3\) and \(y = 3\)) \(\vee\) (\(x = 3\) and \(y = -3\)) \(\vee\) (\(x = 9\) and \(y = 0\)) \(\vee\) (\(x = -9\) and \(y = 1\))
\\
\(\Rightarrow A=\begin{bmatrix}8 & -3 \\ 3 & 2 \end{bmatrix}\) or \(\begin{bmatrix}8 & 3 \\ -3 & 2 \end{bmatrix}\) or \(\begin{bmatrix}8 & 9 \\ -1 & 2 \end{bmatrix}\) or \(\begin{bmatrix}8 & -9 \\ 1 & 2 \end{bmatrix}\). 
\\
With \(A=\begin{bmatrix}8 & -3 \\ 3 & 2 \end{bmatrix}\), we find the corresponding eigenvectors for \(\lambda = 5\). 
\\
\(\Rightarrow \begin{bmatrix}3 & 3 \\ -3 & -3 \end{bmatrix} \begin{bmatrix}k_1 \\ k_2 \end{bmatrix} = \begin{bmatrix}0 \\ 0 \end{bmatrix} \)
\\
\(\Rightarrow  k_1 = k_2\), \(x = \begin{bmatrix} c \\ c \end{bmatrix}\) with \(c \in \mathbb{R}\)
\\
Similarly for other matrices we can have the following result: \\
\(A=\begin{bmatrix}9 & 4 \\ -4 & 1 \end{bmatrix}\) 
\(\Rightarrow  k_1 = k_2\), \(x = \begin{bmatrix} c \\ c \end{bmatrix}\) with \(c \in \mathbb{R}\) \\
\(A=\begin{bmatrix}10 & 5 \\ -5 & 0 \end{bmatrix}\)
\(\Rightarrow  k_1 = k_2\), \(x = \begin{bmatrix} c \\ c \end{bmatrix}\) with \(c \in \mathbb{R}\)
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\end{document}